---
title: "230424_review_rc_datasets"
author: "PR"
date: "2023-04-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      message = F,
                      warning = F)
```

## Goals

There are a lot of RC datasets out there, and it's hard to keep them straight. We are specifically interested in Wenas Creek as our fire-impacted watershed. The goals here are:

1. review what datasets are published, and what they contain
2. review what datasets are in prep and what they contain and 
3. explore what datasets are most useful.


### Background on data packages

In trying to keep this copacetic, I'm only using data published on ESS-DIVE. 

```{r Setup}

require(pacman)
p_load(tidyverse, 
       janitor, 
       cowplot)

theme_set(theme_bw())

```

### SS21 - RC2 Spatial study 2021

We have single measurements available for W10 and W20 from SS21, data types include Manta, MiniDots, and grab samples. 

```{r Read in 21 sensor data}

ss21_manta <- read_csv("data/SFA_SpatialStudy_2021_SensorData_v2/MantaRiver/Plots_and_Summary_Statistics/MantaRiver_Summary_Statistics.csv", skip = 23) %>% 
  clean_names() %>% 
  dplyr::select(site_id, date, temperature_mean, specific_conductance_mean, turbidity_mean, p_h_mean)

ss21_minidot <- read_csv("data/SFA_SpatialStudy_2021_SensorData_v2/MinidotManualChamber/Plots_and_Summary_Statistics/Minidot_Summary_Statistics_v2.csv", skip = 48) %>% 
  clean_names() %>% 
  select(site_id, date, contains("_mean"), matches("^dissolved_oxygen.*slope$")) %>% 
  select(-contains("saturation")) %>% 
    rowwise() %>% 
  mutate(temp_mean = mean(temperature_1_mean, temperature_2_mean, temperature_3_mean), 
         do_mean = mean(dissolved_oxygen_1_mean, dissolved_oxygen_2_mean, dissolved_oxygen_3_mean), 
         do_slope = dissolved_oxygen_1_slope, dissolved_oxygen_2_slope, dissolved_oxygen_3_slope) %>% 
  select(site_id, date, temp_mean, do_mean, do_slope)

ss21_sensors <- full_join(ss21_manta, ss21_minidot, by = c("site_id", "date"))

```


```{r Plot SS21 sensors}

make_ss21_plot <- function(var){
  ss21_sensors %>% 
  filter(grepl("W", site_id)) %>% 
  ggplot(aes(site_id, {{var}})) + 
    geom_col()
}

plot_grid(make_ss21_plot(temp_mean), 
          make_ss21_plot(specific_conductance_mean), 
          make_ss21_plot(turbidity_mean), 
          make_ss21_plot(do_slope), 
          nrow = 1)
          
```


```{r Read in SS21 samples}

ss21_igsns <- tibble(sample_name = c("SPS_0057", "SPS_0058"), 
                     site_id = c("W20", "W10"))

ss21_doc_ions <- read_csv("data/SFA_SpatialStudy_2021_SampleData/SPS_NPOC_TN_DIC_TSS_Ions_Summary.csv") %>% 
  clean_names() %>% 
  rename_all(funs(stringr::str_replace_all(., "mean_[:digit:]{5}_", ""))) %>% 
  select(sample_name, contains("mg_per_l")) %>% 
  mutate(across(everything(), ~replace(., . ==  -9999 , NA)))

ss21_samples <- inner_join(ss21_doc_ions, ss21_igsns, by = "sample_name")

```


```{r Plot SS21 samples}

make_ss21_sample_plot <- function(var){
  ss21_samples %>% 
  ggplot(aes(site_id, {{var}})) + 
    geom_col()
}

plot_grid(make_ss21_sample_plot(dic_mg_per_l_as_c), 
          make_ss21_sample_plot(npoc_mg_per_l_as_c), 
          make_ss21_sample_plot(tn_mg_per_l_as_n), 
          make_ss21_sample_plot(no3_mg_per_l_as_no3), 
          make_ss21_sample_plot(tss_mg_per_l), 
          nrow = 1)
          
```


### TS21 - RC2 Temporal study 2021

It doesn't look like Wenas was sampled, **Is that right??**


### SS22 - Spatial study 2022

```{r Read in sensor data}

ss22_manta <- read_csv("data/SSS_Data_Package/MantaRiver/Plots_and_Summary_Statistics/SSS_Water_Temp_SpC_Turb_pH_ChlA_Summary.csv", skip = 15) %>% 
  clean_names() %>% 
  dplyr::select(site_id, date, temperature_mean, specific_conductance_mean, turbidity_mean, p_h_mean)

ss22_minidot <- read_csv("data/SSS_Data_Package/miniDOTManualChamber/Plots_and_Summary_Statistics/SSS_Water_DO_Temp_Summary.csv", skip = 48) %>% 
  clean_names() %>% 
  select(site_id, date, contains("_mean"), matches("^dissolved_oxygen.*slope$")) %>% 
  select(-contains("saturation")) %>% 
    rowwise() %>% 
  mutate(temp_mean = mean(temperature_1_mean, temperature_2_mean, temperature_3_mean), 
         do_mean = mean(dissolved_oxygen_1_mean, dissolved_oxygen_2_mean, dissolved_oxygen_3_mean), 
         do_slope = dissolved_oxygen_1_slope, dissolved_oxygen_2_slope, dissolved_oxygen_3_slope) %>% 
  select(site_id, date, temp_mean, do_mean, do_slope)

ss22_sensors <- full_join(ss22_manta, ss22_minidot, by = c("site_id", "date"))

```



```{r Plot SS22 sensors}

make_ss22_plot <- function(var){
  ss22_sensors %>% 
  filter(grepl("W", site_id)) %>% 
  ggplot(aes(site_id, {{var}})) + 
    geom_col()
}

plot_grid(make_ss22_plot(temp_mean), 
          make_ss22_plot(specific_conductance_mean), 
          make_ss22_plot(turbidity_mean), 
          make_ss22_plot(do_slope), 
          nrow = 1)
          
```


```{r Read in SS22 samples}

ss22_igsns <- tibble(sample_name = c("SSS024", "SSS036"), 
                     site_id = c("W20", "W10"))

ss22_respiration <- read_csv("data/CM_SSS_Data_Package/CM_SSS_Sediment_Incubations_Respiration_Rates.csv") %>% 
  clean_names() %>% 
  mutate(sample_name = str_sub(sample_name, 1, 6)) %>% 
  select(sample_name, contains("mg_per_l")) 

ss22_doc <- read_csv("data/CM_SSS_Data_Package/CM_SSS_Water_NPOC_TN_Summary.csv") %>% 
  clean_names() %>% 
  rename_all(funs(stringr::str_replace_all(., "mean_[:digit:]{5}_", ""))) %>% 
  select(sample_name, contains("mg_per_l")) %>% 
  mutate(across(everything(), ~replace(., . ==  -9999 , NA)))




ss22_samples <- inner_join(ss22_respiration, ss22_doc, by = "sample_name") %>% 
  inner_join(ss22_igsns, by = "sample_name")

ss22_samples
```

```{r Plot SS21 samples}

make_ss22_sample_plot <- function(var){
  ss22_samples %>% 
  ggplot(aes(site_id, {{var}})) + 
    geom_col()
}

plot_grid(make_ss22_sample_plot(respiration_rate_mg_per_l_per_h), 
          make_ss22_sample_plot(npoc_mg_per_l_as_c), 
          make_ss22_sample_plot(tn_mg_per_l_as_n),  
          nrow = 1)
          
```

### Coming soon

#### RC2 SS22 MiniDot respiration datasets for 1 month


#### RC3 2021-2022 (1+ yr!) grab sampling
collected monthly, grab samples and sensors (Manta, YSI handheld, Ultrameter - no respiration)

#### Left Mantas out through SS22 (maybe a month of data?)


#### Random fire info

2020 Fire: ()
 - W20 burned, and W10 did not
 
2022 - Evans Canyon Fire
 - Both W10 and W20 burned


### Other info informing our assumptions

#### How many samples?
 - 1 - per AMP
 - 2 times min - deploy & retrieve
 - 3 times potentially? - deploy, maintain, retrieve (cotton strips might not last a month)


### What data do we need, and why

- In-situ respiration for as long as possible (Minidot, Barotroll and HOBO) - probably entails a wading transect
- TSS - large change between 21/22 - linked to respiration? (no clear companion analyses)
- DOC/TDN (OCN) - two birds (C and N) w one analytical stone


### Other thoughts: 
- plenty of reaches, including FT, CDOM, Ions, lab respiration (but would be a pain), but above are essentials
- CAVEAT: Don't know what 2021 respiration time-series look like, hard to guess what's important without seeing prior data!



